---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Improving Nutrition Status for under 5 children in Zambezia and Nampula project baseline and endline survey data analysis and reporting workflow

<!-- badges: start -->
[![test analysis workflow](https://github.com/katilingban/zambezia-nampula-survey/actions/workflows/test-analysis-workflow.yaml/badge.svg)](https://github.com/katilingban/zambezia-nampula-survey/actions/workflows/test-analysis-workflow.yaml)
<!-- badges: end -->

This repository is a [`docker`](https://www.docker.com/get-started)-containerised, [`{targets}`](https://docs.ropensci.org/targets/)-based, [`{renv}`](https://rstudio.github.io/renv/articles/renv.html)-enabled [`R`](https://cran.r-project.org/) workflow developed for the data management, data analysis, and reporting of the **Improving Nutrition Status for under 5 Children in Zambezia and Nampula project baseline and endline survey**.


## Repository Structure

* `data/` contains intermediate data outputs produced by the workflow including an endline survey codebook describing all variables of the endline survey;
* `R/` contains functions created for use in this workflow;
* `reports/` contains literate code for R Markdown reports generated in the workflow;
* `outputs/` contains compiled reports and figures;
* `auth/` contains credentials for Google service account (see below for more information);
* `docs/` contains archived high frequency data checks reports produced during the implementation of the survey;
* `did/` contains R script for performing the difference-in-difference analysis using the results tables produced by the analysis pipeline/workflow;
* `_targets.R` file defines the steps in this workflow's data management and analysis pipeline.


## Reproducibility

### R package dependencies

This project requires `R 4.2.2 (2022-11-10 r83330)`. This project uses the `{renv}` framework to record R package dependencies and versions. Packages and versions used are recorded in `renv.lock` and code used to manage dependencies is in `renv/` and other files in the root project directory. On starting an R session in the working directory, `run renv::restore()` to install R package dependencies.

### System requirements

This project's data management and analysis pipeline was built to utilise multi-threaded parallel computing to make calculations faster and more efficient. This project's pipeline uses 4 computing threads. To run without issues, ensure that you use a machine with at least 5 computing threads when reproducing this pipeline (4 threads for the pipeline and the remaininig threads to run the machines regular processes).

With multi-threaded computation, the entire pipeline completes between 30 minutes to an hour (depending on CPU speed and RAM size). Without multi-threading, the entire pipeline completes between 3-5 hours.

### Data management and analysis

This project uses the `{targets}` package to create its data management and analysis pipeline as defined in the `_targets.R` file.

To execute the data management and processing workflow for baseline and endline survey data, run:

```R
targets::tar_make(baseline_data_weighted)
targets::tar_make(endline_data_weighted)
```

The schematic figure below summarises the steps in the data management and processing workflow:

```{r data_management_workflow, echo = FALSE, message = FALSE, results = 'asis'}
cat(
  "```mermaid",
  targets::tar_mermaid(
    targets_only = TRUE, 
    names = c(baseline_data_weighted, endline_data_weighted),
    legend = FALSE
  ),
  "```",
  sep = "\n"
)
```

This produces the following outputs:

* R object for processed baseline data that includes probability weights for use in weighted analysis;
* R object for processed endline data that includes probability weights for use in weighted analysis.

To execute the data analysis workflow for the baseline and endline survey data, run:

```R
targets::tar_make(dplyr::starts_with("baseline"))
targets::tar_make(dplyr::starts_with("endline"))
```

The schematic figure below summarises the steps in the data analysis workflow:

```{r data_analysis_workflow, echo = FALSE, message = FALSE, results = 'asis'}
cat(
  "```mermaid",
  targets::tar_mermaid(
    targets_only = TRUE, 
    #names = c(dplyr::starts_with("overall")),
    #shortcut = TRUE,
    allow = dplyr::contains("results"),
    legend = FALSE
  ),
  "```",
  sep = "\n"
)
```

This pipeline produces the following outputs:

* Baseline results tables in CSV and in XLSX format;
* Baseline results tables subset in CSV format which is used for the difference-in-difference analysis;
* Endline results tables in CSV and in XLSX format;
* Endline results tables subset in CSV format which is used for the difference-in-difference analysis.

These outputs are saved by the pipeline in the `outputs` directory with the following filenames:

* `baseline_results.csv`;
* `baseline_results.xlsx`;
* `baseline_results_subset.csv`;
* `endline_results.csv`;
* `endline_results.xlsx`;
* `endline_results_subset.csv`.

### Difference-in-difference analysis

The **difference-in-difference** analysis was performed using a single `R` script found in the `did/` directory.

To run the **difference-in-difference** analysis, one should first run the data analysis pipeline describe above using the following command in R:

```
targets::tar_make(dplyr::starts_with("baseline"))
targets::tar_make(dplyr::starts_with("endline"))
```
 which will produce the necessary results outputs needed for the **difference-in-difference** analysis.
 
 Then, one should run the **difference-in-difference** R script using the following R command:
 
 ```
 source("did/did.R")
 ```
 
 The outputs of the **difference-in-difference** R script are:
 
 * an HTML file called `analysisDiD.html`;
 * all the plots (in `.png` format) showing the **difference-in-difference** results for each indicator on which the analysis was performed.
 
 
These outputs are saved in the `did/` directory after the **difference-in-difference** R script is run.

This repository doesn't contain the outputs of data management and analysis workflows described above. The user is expected to use this code along with the data from **UNICEF Mozambique** (restricted; request access only; see below) to run the workflows and produce the outputs themselves. All outputs are available from **UNICEF Mozambique** on request. 

 
## Encryption

This repository uses [`git-crypt`](https://github.com/AGWA/git-crypt) to enable transparent encryption and decryption of the `.env` file and the `auth/` directory.

The `.env` file contains:

* variables for authenticating with Google Cloud services account setup for this project for accessing the baseline survey data;

* variables for accessing the endline survey data direct from ONA;

* variables for `SMTP_PASSWORD` and `EMAIL_RECIPIENTS` which are used for sending the email updates for the high frequency data checks.

The `auth/` directory contains credentials for Google service account.

Those who would like to reproduce the results of this project will require ability to decrypt the `.env` file and the `auth/` directory.

To be able to work on this repository, a user/collaborator on this project will need to:

* Create their own **PGP (Pretty Good Privacy) public and private keys**; and,

* Share their public key to the authors and request for it to be added to the repository.

Once added, a collaborator can now decrypt the `.env` file and the `auth/` directory after pulling/cloning the repository by running:

```
git-crypt unlock
```

on the terminal.

## Authors

* Mark Myatt
* Ernest Guevarra

## License
The datasets for both baseline and endline survey (not included in this repository) are owned by **UNICEF Mozambique**. Access to these datasets is restricted. Communicate with **UNICEF Mozambique** to request access to the survey datasets.

The code included in this repository is owned by the authors and is licensed under a [GNU General Public License 3 (GPL-3)](https://opensource.org/licenses/GPL-3.0).

## Feedback

Feedback, bug reports and feature requests are welcome; file issues or seek support [here](https://github.com/katilingban/zambezia-nampula-survey/issues).
